Estimating duration in the presence of misclassification

### 2024-07-29 incidence-prevalence.tex
Rob p52 comment

\emph{Duration}, or \emph{time-to-event}, distributions can be expressed in several equivalent ways~\autocite[17]{sunStatisticala}.
The duration distribution I will be concerned with is the distribution of the duration of detectability.
Consider an individual $i$ infected on day $B_i$ that is prevalent during the interval $[B_i, E_i]$ (as in \cref{E-biology-data:sec:cis-episodes}).
I define this period as an \emph{infection episode}, beginning on day $B_i$ and ending on day $E_i$; therefore, with a duration $D_i = E_i - B_i + 1$.
I model the $D_i$s as a discrete iid (independent and identically distributed) random variables; extending the methodology to account for covariates is left to further work.
The duration is a positive integer, \ie $D_i \in \{1, 2, \dots, \dmax \}$, where $\dmax$ is the maximum duration.
The distribution of $D_i$ can be expressed through the standard probability mass function (pmf), $f_{D}(d) = \prob(D = d)$; or cumulative density function (CDF), $F_{D}(d) = \prob(D \leq d) = \sum_{i=1}^d f_{D}(i)$.
Alternatively, the \emph{survival function} gives the probability that the duration is at least $d$ days: $S(d) = \prob(D \geq d) = 1 - F_{D}(D - 1)$ with $S(1) = 1$.
%(a common alternative convention for survival analysis with discrete variables is to define the survival function as $\prob(D >d)$).
The \emph{hazard} on day $d$ is the probability of recovering on day $d$ conditional on still being positive on day $d$: $\lambda_{d} = \prob(D = d \mid D \geq d) = f_{D}(d) / S(d)$.
Throughout this thesis, the survival function will be the primary quantity of interest, and normally parameterized in terms of the hazard; these two quantities are related by $S(d) = \prod_{i=1}^{d-1} (1 - \lambda_{i})$.

>>>>

\emph{Duration}, or \emph{time-to-event}, distributions can be expressed in several equivalent ways~\autocite[17]{sunStatisticala}.
The duration distribution I will be concerned with is the distribution of the duration of detectability.
Consider an individual $i$ infected on day $B_i$ that is prevalent during the inclusive interval $[B_i, E_i]$ (as in \cref{E-biology-data:sec:cis-episodes}); if $B_i = E_i$ then $i$ is prevalent for exactly one day during which they are detectable.
I define this period as an \emph{infection episode}, beginning on day $B_i$ and ending on day $E_i$; therefore, with a duration $D_i = E_i - B_i + 1$.
I model the $D_i$s as a discrete iid (independent and identically distributed) random variables; extending the methodology to account for covariates is left to further work.
The duration is a positive integer, \ie $D_i \in \{1, 2, \dots, \dmax \}$, where $\dmax$ is the maximum duration.
The distribution of $D_i$ can be expressed through the standard probability mass function (pmf), $f_{D}(d) = \prob(D = d)$; or cumulative density function (CDF), $F_{D}(d) = \prob(D \leq d) = \sum_{i=1}^d f_{D}(i)$.
Alternatively, the \emph{survival function} gives the probability that the duration is at least $d$ days: $S(d) = \prob(D \geq d) = 1 - F_{D}(D - 1)$ with $S(1) = 1$.
%(a common alternative convention for survival analysis with discrete variables is to define the survival function as $\prob(D >d)$).
The \emph{hazard} on day $d$ is the probability of recovering on day $d$ conditional on still being positive on day $d$: $\lambda_{d} = \prob(D = d \mid D \geq d) = f_{D}(d) / S(d)$.
Throughout this thesis, the survival function will be the primary quantity of interest, and normally parameterized in terms of the hazard; these two quantities are related by $S(d) = \prod_{i=1}^{d-1} (1 - \lambda_{i})$.
